---
title: Difference in Proportions Across Groups
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(knitr)
library(kableExtra)
library(purrr)
library(broom)
library(tidytext)
library(wordcloud)
library(RColorBrewer)

# Set global ggplot theme with extra top margin, centered, full-width, bold titles
theme_set(
  theme_minimal() +
    theme(
      plot.margin = margin(t = 30, r = 10, b = 10, l = 10),
      plot.title.position = "plot",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),  # Center the subtitle
      legend.position = "none"  # Hide legend globally
    )
)



# Load data
all_responses_all_questions <- read_excel("all_responses_all_questions.xlsx")

# Reshape to long format including counts and proportions
all_responses_all_questions_long <- all_responses_all_questions %>%
  select(
    Question, Category, Label.y, Level,
    Count_overall, Count_tenure, Count_nontenure,
    Proportion_nonNA_overall, Proportion_nonNA_tenure, Proportion_nonNA_nontenure
  ) %>%
  pivot_longer(
    cols = starts_with("Count_") | starts_with("Proportion_nonNA_"),
    names_to = c(".value", "Group"),
    names_pattern = "(.*)_(overall|tenure|nontenure)"
  ) %>%
  mutate(
    Group = recode(Group,
      "overall"    = "Overall",
      "tenure"     = "Tenure Track",
      "nontenure"  = "Non-tenure Track"
    ),
    Group = factor(Group, levels = c("Overall", "Tenure Track", "Non-tenure Track"))
  )

# Define group colors
group_colors <- c(
  "Overall"          = "#1F78B4",  # dark blue
  "Tenure Track"     = "#E66101",  # dark orange
  "Non-tenure Track" = "#4DAF4A"   # dark green
)

```

*The following analyses only include questions with statistically significant differences between responses in groups at the 0.05 alpha level using Chi Square and Fisher's Exact tests. Difference in proportions tests were then applied to get a general idea of which category had significant differences.*

## Tenure Track and Non-tenure Track


<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Rank and Title</h3>
</div>



```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Define the specific questions you want
selected_questions <- c("_v8", "_v9")

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
rank_title_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Rank/Title",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    Question %in% selected_questions
  )

# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(rank_title_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- rank_title_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```



<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Retitling Process</h3>
</div>



```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
retitling_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Retitling Process",
    Level != "NA",
    !str_detect(Label.y, "Other - Text")
  )

# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(retitling_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- retitling_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```



<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Service</h3>
</div>



```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
service_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Service",
    Question != "_v43",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    !str_detect(tolower(Label.y), "how many")  # excludes anything containing "how many"
  )


# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(service_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- service_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```

```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Define the specific questions you want
selected_questions <- c("_v43")

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
serv_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Service",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    Question %in% selected_questions
  )

# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(serv_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- serv_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```



<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Professional development/promotion</h3>
</div>




```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
profdev_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Professional development and promotion",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    !str_detect(tolower(Label.y), "how many")  # excludes anything containing "how many"
  )

# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(profdev_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- profdev_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```



<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Well-being</h3>
</div>



```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
profdev_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Well-being",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    !str_detect(tolower(Label.y), "how many")  # excludes anything containing "how many"
  )


# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(profdev_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- profdev_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
tab <- subset %>%
  select(Level, Group, Count) %>%
  group_by(Level, Group) %>%
  summarise(
    Total = sum(Count, na.rm = TRUE),   # <— here
    .groups = "drop"
  ) %>%
  pivot_wider(names_from = Group, values_from = Total, values_fill = 0)

  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```



<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Equity, morale, respect, and satisfaction</h3>
</div>



```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
equity_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Equity, morale, respect, and satisfaction",
    Question != "_v91",
    Question != "_v92",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    !str_detect(tolower(Label.y), "how many")  # excludes anything containing "how many"
  )


# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(equity_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- equity_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
tab <- subset %>%
  select(Level, Group, Count) %>%
  group_by(Level, Group) %>%
  summarise(
    Total = sum(Count, na.rm = TRUE),   # <— here
    .groups = "drop"
  ) %>%
  pivot_wider(names_from = Group, values_from = Total, values_fill = 0)

  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Define the specific questions you want
selected_questions <- c("_v91", "_v92")

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
eq_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Equity, morale, respect, and satisfaction",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    Question %in% selected_questions
  )

# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(eq_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- eq_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```




<div style="background-color: black; color: white; padding: 10px; margin-bottom: 10px;">
<h3>Effort Distribution</h3>
</div>



```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}

# Filter for Rank/Title category, exclude Level == "NA", exclude 'Other - Text', and include only selected questions
effort_data <- all_responses_all_questions_long %>%
  filter(
    Category == "Effort Distribution",
    Level != "NA",
    !str_detect(Label.y, "Other - Text"),
    !str_detect(tolower(Label.y), "how many")  # excludes anything containing "how many"
  )


# Step 1: Run chi-squared or Fisher test per question, keep significant ones
unique_questions <- unique(effort_data$Question)

chi_results <- list()

for (q in unique_questions) {
  
  subset <- effort_data %>%
    filter(Question == q, Group %in% c("Tenure Track", "Non-tenure Track"))
  
  tab <- subset %>%
    select(Level, Group, Count) %>%
    group_by(Level, Group) %>%
    summarise(Total = sum(Count), .groups = "drop") %>%
    pivot_wider(names_from = Group, values_from = Total, values_fill = 0)
  
  if (nrow(tab) >= 2) {
    mat <- as.matrix(tab[, c("Tenure Track", "Non-tenure Track")])
    rownames(mat) <- tab$Level
    
    test <- if (any(chisq.test(mat)$expected < 5)) {
      fisher.test(mat)
    } else {
      chisq.test(mat)
    }
    
    if (test$p.value < 0.05) {
      chi_results[[q]] <- list(
        question_label = unique(subset$Label.y),
        data = tab,
        total_TT = sum(tab$`Tenure Track`),
        total_NTT = sum(tab$`Non-tenure Track`)
      )
    }
  }
}
```


```{r, fig.height = 10, fig.width = 7, echo=FALSE, warning=FALSE, message=FALSE}
# Step 2: For significant questions, run pairwise proportion tests
pairwise_list <- list()

for (entry in chi_results) {
  tab <- entry$data
  tt_total <- entry$total_TT
  ntt_total <- entry$total_NTT
  
  pvals <- map_dbl(1:nrow(tab), function(i) {
    prop.test(x = c(tab$`Tenure Track`[i], tab$`Non-tenure Track`[i]),
              n = c(tt_total, ntt_total))$p.value
  })
  
  adj_pvals <- p.adjust(pvals, method = "holm")
  
  pairwise_list[[entry$question_label]] <- data.frame(
    Question = entry$question_label,
    Response = tab$Level,
    `TT Count` = tab$`Tenure Track`,
    `NTT Count` = tab$`Non-tenure Track`,
    `Raw p-value` = round(pvals, 3)
  )
}

# Combine all pairwise results into a single dataframe
final_table <- bind_rows(pairwise_list) %>%
  arrange(Question, Response) %>%
  rename(
    `TT Count`    = TT.Count,
    `NTT Count`   = NTT.Count,
    `P-value` = Raw.p.value
  ) %>%
  select(-Question)  # DROP the Question column (will use pack_rows)

# Create base kable
kbl_obj <- kbl(final_table, format = "html", digits = 4, align = "c") %>%
  kable_styling(
    bootstrap_options = c("hover", "condensed", "bordered"),
    full_width = FALSE,
    position = "center"
  )

# Add grouped row blocks by Question (from original data)
unique_questions <- unique(bind_rows(pairwise_list)$Question)
start_row <- 1

for (q in unique_questions) {
  n_rows <- sum(bind_rows(pairwise_list)$Question == q)
  kbl_obj <- kbl_obj %>%
    pack_rows(group_label = q, start_row, start_row + n_rows - 1, bold = TRUE)
  start_row <- start_row + n_rows
}

# Print final table
kbl_obj
```
