---
title: ""
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(knitr)
library(kableExtra)
library(purrr)
library(broom)
library(tidytext)
library(wordcloud)
library(RColorBrewer)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
word_qs <- read_excel("Word_questions.xlsx")
```


<div style="text-align: center;">
<h1>Welcome!</h1>
</div>


<div style="text-align: center;">

*This site presents a set of summaries from the 2025 faculty survey.*

</div>


<div style="text-align: center;">

*Explore the sections below to learn about responses on demographics, job satisfaction, equity, and more.*

</div>


<div style="text-align: left;">
<h1>Sections:</h1>
</div>

- [Proportions of Responses](proportions.html): Compare response proportions among the overall sample, Tenure Track and Non-tenure Track, and among different groups that are Non-tenure Track. Questions are grouped as per original survey sections. 
    
    

- [Differences Between Groups](differences.html): Tests of differences between Tenure and Non-Tenure respondents. 
    
    

- [Free-write Responses](free-write.html): Summaries of what people wrote in the free-write responses. 


- [General Information](gen-info.html): Summary of survey times, completion rates, and sample sizes.


<div style="text-align: center;">


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# 2) Tokenize into words, weight by your Count column
words <- word_qs %>%
  unnest_tokens(word, Level) %>%
  filter(word != "5") %>%  
  filter(word != "1") %>%  
    filter(word != "3") %>% 
    filter(word != "4") %>% 
  filter(word != "2") %>%  
  filter(word != "e.g") %>% 
  filter(word != "100") %>% 
  count(word, wt = Count, sort = TRUE)

# 3) Remove stop words
data("stop_words")
words_nostop <- words %>%
  anti_join(stop_words, by = "word")

# 4) Draw the wordcloud
set.seed(2025)  # for reproducibility
with(
  words_nostop,
 wordcloud(
  words      = word,
  freq       = n,
  max.words  = 200,
  random.order = FALSE,
  colors     = brewer.pal(8, "Dark2"),
  scale      = c(7, 0.5)  # make words bigger!
)

)
```